Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels

### 2018-04-27 articles/formalism/sections/kernel_discussion.tex
added a section relating the spin raising/lowering operators to real space operators
generated a proper sign version of the codes, generated the convolution kernel plots and added them to the pape. the kernel plots are updated to have the proper sign.

\subsection{Visualizing the convolution kernels} \label{sec:visualize_operator}
%
\begin{figure}[t] \label{fig:mixing_kernel}
\centering
%\captionsetup[subfigure]{labelformat=empty}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat90_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat90_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat90_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat90_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat90_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat90_lon45.pdf}}\\[-2ex]
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat87_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat87_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat87_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat87_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat87_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat87_lon45.pdf}}\\[-2ex]
%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat87_lon30.pdf}}\\[-2ex]
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat80_lon30.pdf}}\\[-2ex]
\subfigure[$\mathcal{M}_r$]{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\mathcal{M}_i$]{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\mathcal{D}_r$]{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\mathcal{D}_i$]{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\mathcal{I}_r$]{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\mathcal{I}_i$]{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat0_lon90.pdf}}
\caption{This panel of figure depicts the various parts of the convolution kernel, discussed in \sec{sec:real_space_operators}. These kernels have been evaluated with the band limit: $\ell \in [2,192]$ but sampled at the Healpix resolution parameter NSIDE=2048 for visual appeal. The size of each panel is approximately $16^{\circ} \times 16^{\circ}$ and the grid lines are marked at 2 degree separations. The black circles denotes the position of the central pixel around which the convolution kernels have been evaluated while the black star marks the location of the north galactic pole. The four rows depict the kernels at different location on the sphere and the galactic coordinates of the central pixel are specified in each panel.}
%from top to bottom rows are as follows $[b,\ell] = [0^{\circ},0^{\circ}], [87^{\circ},0^{\circ}], [87^{\circ},30^{\circ}], [80^{\circ},30^{\circ}], [0^{\circ},90^{\circ}]$.}
\label{fig:vis_kernel}
 \end{figure}
%

@@

\subsection{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
%
\begin{figure}[!hbt]
\centering
\includegraphics[width=0.8\columnwidth]{kernel/beta_kernel.pdf}
\caption{The figure depicts the radial part of the convolution kernels. These radial function have been evaluated with the band limit fixed at $\ell \in [2,24]$. The vertical dashed line marks the approximate Healpix pixel size of a NSIDE=8, which is the lowest resolution that allows access to $\ell_{\rm max}=24$.}
\label{fig:beta_kernel}
\end{figure}
%
\fig{fig:mixing_kernel} and the surrounding discussion provides a quantative understanding of the  azimuthal dependence of various kernels, however it is difficult to assess the radial nature of these kernels from these figures. The radial part determines the non-locality of the respective operators and encodes all the multipole dependence. We compute the radial kernels ${_{\mm}f}, {_{\md}f} ~\&~ {_{\mi}f} $ by evaluating the respective multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,192]$ and the resultant functions are depicted in \fig{fig:beta_kernel}.

Recall that ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$ \& $U$ to scalars $E$ \& $B$ and vice versa. Note that ${_{\mm}f}$ has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$) as seen in \fig{fig:beta_kernel} and one can show that that ${_{\mm}f(\beta=\pi)}=0$. The coordinate dependence of the Stokes parameters cannot be integrated out in the vicinity of the locations $\beta=0,\pi$ due to the fact that the azimuthal angles become ill defined here therefore this nature of ${_{\mm}f}$ is necessary to ensure that the derived fields behave as scalars. Similarly while deriving the Stoke field from the scalars $E$ \& $B$ this nature of ${_{\mm}f}$ is necessary to ensure that the necessary coordinate dependencies are integrated in. ${_{\md}f}$ shows a similar behaviour, it has a vanishing contribution in the vicinity of the central pixel and dominantly contributes in regions which are approximately at least 1 pixel distance away from the central pixel as seen in \fig{fig:beta_kernel}. ${_{\mi}f}$ is the radial part of the band limited delta function $\mi$ and expectedly contributes the most at the location of the central pixel.

\noindent \textit{The band limit dependence:} It is clear from previous discussions that the scalar field $E$ \& $B$ constructed at a location depends on the Stokes field in the surrounding regions. We further quantify this non-locality by studying the radial extent of the kernels and its dependence on the maximum multipole accessible for analysis. To carry out this study we evaluate the radial functions for different values of $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$. 
%
\begin{figure}[t]
\centering
\subfigure{\includegraphics[width=0.96\columnwidth]{kernel/f_rad_ker_fn_of_ellmax.pdf}}
\subfigure{\includegraphics[width=0.48\columnwidth]{kernel/fm2_rad_ker_fn_of_ellmax.pdf}}
\subfigure{\includegraphics[width=0.48\columnwidth]{kernel/fp2_rad_ker_fn_of_ellmax.pdf}}
\caption{The top panel depicts the radial function  ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for fixed $\ell_{\rm min}=2$ and different $\ell_{\rm max}$ as indicated by their legends. All the curves have been normalized such that the maximum of the curve is set to unity. The horizontal solid black line marks the location where the amplitude of the kernel falls below 1\% of its maximum. The slanted dashed black lines indicate a power law fit (by eye) to the envelope of the radial functions. While the envelopes for function ${_{\mm}f}(\beta)~\&~ {}_{\mi}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{\md}f(\beta)$ is seen to have a slightly steeper slope $\propto \beta^{-1.65}$.}
\label{fig:rad_ker_decay}
\end{figure}
%
The resultant set of radial function are depicted in \fig{fig:rad_ker_decay}, where all the function have been normalized such that their global maxima is set to unity. We note that on increasing $\ell_{\rm max}$ the radial kernels shift left, attaining their global maxima at progressively small angular distance from the central pixel. The amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$. At intermediate values of $\beta$, the envelope of the radial functions is fit well by a power law $ \propto \beta^{-n}$, the details of this fit can be seen in \fig{fig:rad_ker_decay}.
We observe that the radial functions computed by evaluating the multipole sums to different maximum multipoles are self similar and follow an interesting telescoping and scaling property, $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell_{\rm max}}{\ell'_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions. 
%We can understand the shifting left of the radial kernels on increasing the maximum multipole using this property. Lets say the function ${}_rf(\beta, \ell'_{\rm max})$ transition to being monotonously below some fraction of the global maxima at an angular distance of $\beta_0$.  The function ${}_rf(\beta', \ell_{\rm max})$, given $\ell_{\rm max} > \ell'_{\rm max}$, reaches the same transition point $\beta'=\beta_0$ at a smaller value of $\beta$ owing to the fact that $\ell_{\rm max}/\ell'_{\rm max}$ is greater than unity. The amplitude scaling of the functions is irrelevant since the transition point is always described in terms of the fraction of the global maxima of the function.

>>>>

\subsection{Visualizing the convolution kernels} \label{sec:visualize_operator}
%
\begin{figure}[t] \label{fig:mixing_kernel}
\centering
\captionsetup[subfigure]{labelformat=empty}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat90_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat90_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat90_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat90_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat90_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat90_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat90_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat90_lon45.pdf}}\hspace{-2mm}

\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat87_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat87_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat87_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat87_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat87_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat87_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat87_lon45.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat87_lon45.pdf}}\hspace{-2mm}

\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure[$ \textrm{Re} \left(\mathcal{M}_{G} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\textrm{Img} \left(\mathcal{M}_{G} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\textrm{Re}  \left(\mathcal{M}_{B} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\textrm{Img} \left(\mathcal{M}_{B} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\textrm{Re} \left(\mathcal{D} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\textrm{Img} \left(\mathcal{D} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\textrm{Re} \left(\mathcal{I} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\textrm{Img} \left(\mathcal{I} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat0_lon90.pdf}}\hspace{-2mm}
\caption{This panel of figure depicts the various parts of the convolution kernel, discussed in \sec{sec:real_space_operators}. These kernels have been evaluated with the band limit: $\ell \in [2,192]$ but sampled at the Healpix resolution parameter NSIDE=2048 for visual appeal. The size of each panel is approximately $16^{\circ} \times 16^{\circ}$ and the grid lines are marked at 2 degree separations. The black circles denotes the position of the central pixel around which the convolution kernels have been evaluated while the black star marks the location of the north galactic pole. The four rows depict the kernels at different location on the sphere and the galactic coordinates of the central pixel are specified in each panel.}
%from top to bottom rows are as follows $[b,\ell] = [0^{\circ},0^{\circ}], [87^{\circ},0^{\circ}], [87^{\circ},30^{\circ}], [80^{\circ},30^{\circ}], [0^{\circ},90^{\circ}]$.}
\label{fig:vis_kernel}
 \end{figure}
%

@@

\subsection{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
%
\begin{figure}[t]
\centering
\includegraphics[width=0.8\columnwidth]{kernel/beta_kernel.pdf}
\caption{The figure depicts the radial part of the convolution kernels. These radial function have been evaluated with the band limit fixed at $\ell \in [2,24]$. The vertical dashed line marks the approximate Healpix pixel size of a NSIDE=8, which is the lowest resolution that allows access to $\ell_{\rm max}=24$.}
\label{fig:beta_kernel}
\end{figure}
%
\fig{fig:mixing_kernel} and the surrounding discussion provides a quantative understanding of the  azimuthal dependence of various kernels, however it is difficult to assess the radial nature of these kernels from these figures. The radial part determines the non-locality of the respective operators and encodes all the multipole dependence. We compute the radial kernels ${_{\mm}f}, {_{\md}f} ~\&~ {_{\mi}f} $ by evaluating the respective multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,192]$ and the resultant functions are depicted in \fig{fig:beta_kernel}. 
%
\begin{figure}[t]
\centering
\subfigure{\includegraphics[width=0.96\columnwidth]{kernel/f_rad_ker_fn_of_ellmax.pdf}}
\subfigure{\includegraphics[width=0.48\columnwidth]{kernel/fm2_rad_ker_fn_of_ellmax.pdf}}
\subfigure{\includegraphics[width=0.48\columnwidth]{kernel/fp2_rad_ker_fn_of_ellmax.pdf}}
\caption{The top panel depicts the radial function  ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for fixed $\ell_{\rm min}=2$ and different $\ell_{\rm max}$ as indicated by their legends. All the curves have been normalized such that the maximum of the curve is set to unity. The horizontal solid black line marks the location where the amplitude of the kernel falls below 1\% of its maximum. The slanted dashed black lines indicate a power law fit (by eye) to the envelope of the radial functions. While the envelopes for function ${_{\mm}f}(\beta)~\&~ {}_{\mi}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{\md}f(\beta)$ is seen to have a slightly steeper slope $\propto \beta^{-1.65}$.}
\label{fig:rad_ker_decay}
\end{figure}
%
Recall that ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$ \& $U$ to scalars $E$ \& $B$ and vice versa. Note that ${_{\mm}f}$ has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$) as seen in \fig{fig:beta_kernel} and one can show that that ${_{\mm}f(\beta=\pi)}=0$. The coordinate dependence of the Stokes parameters cannot be integrated out in the vicinity of the locations $\beta=0,\pi$ due to the fact that the azimuthal angles become ill defined here therefore this nature of ${_{\mm}f}$ is necessary to ensure that the derived fields behave as scalars. Similarly while deriving the Stoke field from the scalars $E$ \& $B$ this nature of ${_{\mm}f}$ is necessary to ensure that the necessary coordinate dependencies are integrated in. ${_{\md}f}$ shows a similar behaviour, it has a vanishing contribution in the vicinity of the central pixel and dominantly contributes in regions which are approximately at least 1 pixel distance away from the central pixel as seen in \fig{fig:beta_kernel}. ${_{\mi}f}$ is the radial part of the band limited delta function $\mi$ and expectedly contributes the most at the location of the central pixel.

\noindent \textit{The band limit dependence:} It is clear from previous discussions that the scalar field $E$ \& $B$ constructed at a location depends on the Stokes field in the surrounding regions. We further quantify this non-locality by studying the radial extent of the kernels and its dependence on the maximum multipole accessible for analysis. To carry out this study we evaluate the radial functions for different values of $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.

The resultant set of radial function are depicted in \fig{fig:rad_ker_decay}, where all the function have been normalized such that their global maxima is set to unity. We note that on increasing $\ell_{\rm max}$ the radial kernels shift left, attaining their global maxima at progressively small angular distance from the central pixel. The amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$. At intermediate values of $\beta$, the envelope of the radial functions is fit well by a power law $ \propto \beta^{-n}$, the details of this fit can be seen in \fig{fig:rad_ker_decay}.
We observe that the radial functions computed by evaluating the multipole sums to different maximum multipoles are self similar and follow an interesting telescoping and scaling property, $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell_{\rm max}}{\ell'_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions. 
%We can understand the shifting left of the radial kernels on increasing the maximum multipole using this property. Lets say the function ${}_rf(\beta, \ell'_{\rm max})$ transition to being monotonously below some fraction of the global maxima at an angular distance of $\beta_0$.  The function ${}_rf(\beta', \ell_{\rm max})$, given $\ell_{\rm max} > \ell'_{\rm max}$, reaches the same transition point $\beta'=\beta_0$ at a smaller value of $\beta$ owing to the fact that $\ell_{\rm max}/\ell'_{\rm max}$ is greater than unity. The amplitude scaling of the functions is irrelevant since the transition point is always described in terms of the fraction of the global maxima of the function.
